Technical Report

### 2018-03-14 fully-abstract-comp/technical-report.tex
started a list of compilation assumptions for the FTLR.
Spatial regions can evolve into spatial_owned ones.
Add the notion of the purePart of a world to the main file.

% For both $\privft$ and $\pubft$ we have
% \begin{mathpar}
%   \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \future W(r) }
%             { W' \future W }
% \end{mathpar}
%
The private future regions allow transitions in the private part of the transition system. They also allow $\spatial$ regions to become $\revoked$:
\begin{mathpar}
  \inferrule{ }
  { \revoked \privft (\spatial,\_,\_,\_,\_)}
\and
  \inferrule{ }
            { \revoked \privft \revoked }
\and
  \inferrule{ (s,s') \in \phi }
            { (v,s',\phi_\pub,\phi,H) \privft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}
%
Public future regions are allowed to transition according to the public part of their transition system.
\begin{mathpar}
    \inferrule{ }
            { \revoked \pubft \revoked }
\and
  \inferrule{ (s,s') \in \phi_\pub }
            { (v,s',\phi_\pub,\phi,H) \pubft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}

>>>>

% For both $\privft$ and $\pubft$ we have
% \begin{mathpar}
%   \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \future W(r) }
%             { W' \future W }
% \end{mathpar}
%
The private future regions allow transitions in the private part of the transition system. They also allow $\spatial$ regions to become $\revoked$.
Also: both future region relations allow $\spatial$ regions to become $\spatialo$, which expresses that our system is affine, rather than linear.
\begin{mathpar}
  \inferrule{ }
  { \revoked \privft (\spatial,\_,\_,\_,\_)}
\and
  \inferrule{ }
            { \revoked \privft \revoked }
            \and
    \inferrule{ }
            { \spatialo \privft \spatial }
\and
  \inferrule{ (s,s') \in \phi }
            { (v,s',\phi_\pub,\phi,H) \privft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}
%
Public future regions are allowed to transition according to the public part of their transition system.
\begin{mathpar}
    \inferrule{ }
            { \revoked \pubft \revoked }
            \and
    \inferrule{ }
            { \spatialo \pubft \spatial }
\and
  \inferrule{ (s,s') \in \phi_\pub }
            { (v,s',\phi_\pub,\phi,H) \pubft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}

\begin{definition}[The pure part of a world]
  For any world $W$, we define
  \begin{align*}
    \purePart{W} &\defeq (\purePart{\pwheap},\purePart{\pwpriv},\purePart{\pwfree})\\
    \purePart{W_\var{heap}} &\defeq
                       \begin{cases}
                         W_{\var{heap}}(r) & \text{if } W_\var{heap}(r) = (pure,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_\var{heap}(r) = (\spatial,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_\var{heap}(r) = (\spatialo,\var{sm})\\
                         \revoked & \text{if } W_\var{heap}(r) = \revoked\\
                       \end{cases}\\
    \purePart{W_\var{priv}} &\defeq
                       \begin{cases}
                         ((\spatial,\var{sm}),\sigma) & \text{if } W_\var{priv}(r) = ((\spatial,\var{sm}),\sigma)\\
                         ((\spatial,\var{sm}),\sigma) & \text{if } W_\var{priv}(r) = ((\spatialo,\var{sm}),\sigma)\\
                         (\revoked,\sigma) & \text{if } W_\var{priv}(r) = (\revoked,\sigma)\\
                       \end{cases}\\
    \purePart{W_\var{free}} &\defeq
                       \begin{cases}
                         W_{\var{free}}(r) & \text{if } W_{\var{free}}(r) = (pure,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_{\var{free}}(r) = (\spatial,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_{\var{free}}(r) = (\spatialo,\var{sm})\\
                         \revoked & \text{if } W_{\var{free}}(r) = \revoked\\
                       \end{cases}
  \end{align*}
\end{definition}

\begin{lemma}[purePart is duplicable]
  \label{lem:purePart-duplicable}
 For all $W$, we have that $W = W \oplus \purePart{W}$.
\end{lemma}

\begin{lemma}[Increasing authority is the future]
  \label{lem:oplus-future}
  For all $W$, we have that:
  $W_1 \oplus W_2 \future W_1$
\end{lemma}

\begin{lemma}[Purity is a thing of the past]
  \label{lem:world-fut-purePart}
  For all $W$, we have that $W \future \purePart{W}$.
\end{lemma}
\begin{proof}
  Direct consequence of Lemmas~\ref{lem:purePart-duplicable}
  and~\ref{lem:oplus-future}.
\end{proof}
